\textbf{NBA Party}

### 2017-06-11 init_model.rnw
Added plots for density-of-travel-dist-by-party and also heat-map-of-next-day-opponenty-by-last-game-location.

HOURS <- 24
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) & 
                nhours.lgame <= HOURS & 
                last.game.loc != team]

@@

tmp <- musicians[, list(party.continuous = mean(log(nmusicians+1))), 
                 by = team][order(party.continuous)][!is.na(party.continuous)]

##################################################
### Dot plot of Party-Continuous by Team Location
##################################################
pdf('writing/Party_by_Team_Location.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location',
     ylab = 'Log Avg of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
## text(x = ticks, y = 1.25, labels = tmp$team, srt = 90)
axis(side = 2)
dev.off()

@@

mpa <- lm(team.pts.admitted ~ party + lag.chg.pos + log(travel.dist+1) + nhours.lgame, 
   data=nba.lines[last.game.loc!=team] %>% na.omit)
mpo <- update(mpa, team.pts.scored ~ .)

### Points  allowed as afunction of last game location (by party)
nba.lines[, demeaned.pts.admitted := team.pts.admitted - mean(team.pts.admitted), by = list(season, team)]
nba.lines[, mean(demeaned.pts.admitted), by = list(last.game.loc, party.discrete)][order(V1)]
mpa1 <- lm(demeaned.pts.admitted ~ party.discrete, data = nba.lines)
#stargazer(mpa1, mpa, mpo, single.row=T)

tmp <- nba.lines[, list(demeaned.pts.admitted = mean(demeaned.pts.admitted)), 
                 by = list(last.game.loc, party)][order(demeaned.pts.admitted)]
plot(x=jitter(tmp$party),y=tmp$demeaned.pts.admitted)
abline(lm(demeaned.pts.admitted ~ party, data=tmp))
#stargazer(m, style = 'qje', single.row = T)
## stargazer(m)

@@

mlb.lines[, party.discrete := grepl("(los angeles)|(new york)", last.game.loc) & ndays.lgame == 1 & weekend == T]
#stargazer(m0, m1, m2, m3, single.row = T)
@

@@

pdf('mlb_bets_by_season.pdf')
par(mfrow = c(3,2))
b <- lapply(2012:2016, function(yr) {
    m <- glm(I(team.score > opponent.score) ~ party + odds,
             data = mlb.lines[year(date) < yr], family = 'binomial')
    p <- predict(m, newdata = mlb.lines[year(date) == yr], type = 'response')
    idx <- which(p < .45)
    p1 <- mapply(Predict, prediction = p[idx], 
                 vegas = mlb.lines[year(date) == yr, odds][idx],
                 MoreArgs=list(threshold = 0.01))
    b <- mapply(Bet, our.prediction = p1,
                actual.outcome = mlb.lines[year(date) == yr, team.score > opponent.score][idx],
                odds = mlb.lines[year(date) == yr, odds][idx], SIMPLIFY = T)
    cat(paste0(sum(b, na.rm = T), '\n'))
    ### 
#    pdf(paste0('mlb_bets_', yr, '.pdf'))
    betting.days <- mlb.lines[year(date) == yr][idx, date]
    running.prof <- cumsum(ifelse(is.na(b), 0, b))
    plot(x = 1:length(b), y = running.prof, 
         main = paste0('Profits over the ', yr, ' season\n',
                       'Training on 2011-', yr-1, ' data'),
         xlab = 'Game Number', ylab = 'Profit', type = 'l')
    abline(a = 0, b = 0, lty = 3)
    points(x = which.min(running.prof), y = min(running.prof), type = 'p')
    text(x = which.min(running.prof), y = min(running.prof), 
         labels = round(min(running.prof)), pos = 4)
    return(b)
#    dev.off()
})
dev.off()

>>>>

HOURS <- 24
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) & 
                nhours.lgame <= HOURS & 
                last.game.loc != team]
nba.lines[, party.placebo := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) & 
                nhours.lgame > HOURS & 
                last.game.loc != team]

@@

##################################################
### Dot plot of Party-Continuous by Team Location
##################################################
tmp <- musicians[, list(party.continuous = mean(log(nmusicians+1))), 
                 by = team][order(party.continuous)][!is.na(party.continuous)]

pdf('writing/Party_by_Team_Location.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location: NBA',
     ylab = 'Log Avg of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
## text(x = ticks, y = 1.25, labels = tmp$team, srt = 90)
axis(side = 2)
dev.off()

##################################################
### Histogram of travel dist by party vs not
##################################################
pdf('writing/travel_dist_by_party.pdf', width = 11, height = 8.5)
par(mfrow = c(2,1))
hist(x = nba.lines[party.discrete == F, travel.dist], 
     main = 'Histogram of Travel Distance by Last Game Location', xlab = '')
legend(x = 2250, y = 3500, legend = c('Non Party Cities', 'LA and NY'), 
       col = c('white', 'black'), fill = c(F, T))
hist(x = nba.lines[party.discrete == T, travel.dist], 
     main = '', col = 'black', xlab = 'Travel Distance')
dev.off()

pdf('writing/travel_dist_density_by_party.pdf', width = 12, height = 11)
plot(density(nba.lines[(party.discrete) & !is.na(travel.dist), travel.dist]), 
     xlim = c(-100, 18e2), lty = 1,
     main = 'Density of travel distance\nfor (non) party cities: NBA',
     xlab = 'Travel Distance (Miles)')
lines(density(nba.lines[!(party.discrete) & !is.na(travel.dist), travel.dist]), lty = 2)
legend(x = 15e2, y = 0.0015, legend = c('LA/NY', 'non-party cities'), lty = 1:2)
dev.off()

##################################################
### Placebo model
##################################################
mp <- update(m0, . ~ party.placebo + . - party.discrete)

stargazer(mp, covariate.labels = c('party placebo', 'lag changes in posession', 'logged travel distance', 'east-west travel direction', 'number hours rest time', 'time of game during day', 'home team effect', 'logged travel distance * east-west', 'Constant'),
          dep.var.labels = 'Meet the Spread')

##################################################
### Table for uncorrelated next day opponent
##################################################

tmp <- nba.lines[, .N, 
                 keyby = list(location, last.game.loc, 
                              cur.game = paste('Current game', 
                                               ifelse(location == team, 'at home', 'away')),
                              lst.game = paste('Last game',
                                               ifelse(last.game.loc == team, 'at home', 'away')))] %>% 
    na.omit

pdf('writing/next_day_opponent.pdf', width = 14, height = 14)
ggplot(tmp, aes(x = location, y = last.game.loc, fill = log(N))) + 
    geom_tile() +
    facet_wrap(~lst.game + cur.game) + 
    labs(x = 'Current Game Location', y = 'Last Game Location', 
         title = 'Distribution of Next Day Opponent - NBA') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 315, vjust = 0.5),
          plot.title = element_text(hjust=.5))
dev.off()

@@

tpa <- lm(team.pts.admitted ~ party + lag.chg.pos + log(travel.dist+1) + nhours.lgame, 
   data=nba.lines[last.game.loc!=team] %>% na.omit)
tpo <- update(tpa, team.pts.scored ~ .)

### Points  allowed as afunction of last game location (by party)
nba.lines[, demeaned.pts.admitted := team.pts.admitted - mean(team.pts.admitted), by = list(season, team)]
nba.lines[, mean(demeaned.pts.admitted), by = list(last.game.loc, party.discrete)][order(V1)]
mpa1 <- lm(demeaned.pts.admitted ~ party.discrete, data = nba.lines)

stargazer(mpa1, tpa, tpo, dep.var.labels = c('Points Admitted by Team', 'Team Points Admitted', 'Team Points Scored'),
          covariate.labels = c('Discrete party indicator',
                               'Continuous party measure',
                               'Lag change in possessions',
                               'Logged travel distance',
                               'Number hours since last game',
                               'Constant'))

stargazer(m2, dep.var.labels = 'Demeanead Rebounds Per Minute',
          covariate.labels = c('Continuous party measure',
                               'Lag change in possessions',
                               'Logged travel distance',
                               'Number hours since last game',
                               'Constant'))

## tmp <- nba.lines[, list(demeaned.pts.admitted = mean(demeaned.pts.admitted)), 
##                  by = list(last.game.loc, party)][order(demeaned.pts.admitted)]
## plot(x=jitter(tmp$party),y=tmp$demeaned.pts.admitted)
## abline(lm(demeaned.pts.admitted ~ party, data=tmp))
## #stargazer(m, style = 'qje', single.row = T)
## ## stargazer(m)

@@

mlb.lines[, party.discrete := grepl("(los angeles)|(new york)", last.game.loc) & ndays.lgame == 1 & weekend == T]

## stargazer(m3, covariate.labels = c('Continuous measure of nightlife',
##                                    'Bookmaker\'s odds', 'Home-team effect',
##                                    'Number of rest days', 'Logged travel distance',
##                                    'Weekend', 'Constant'), 
##           dep.var.capation = 'Probability of Winning')

##################################################
### Heat Map for next day opponent
##################################################
tmp <- mlb.lines[, .N, 
                 keyby = list(location, last.game.loc, 
                              cur.game = paste('Current game', 
                                               ifelse(location == team, 'at home', 'away')),
                              lst.game = paste('Last game',
                                               ifelse(last.game.loc == team, 'at home', 'away')))] %>% 
    na.omit

pdf('writing/next_day_opponent_mlb.pdf', width = 14, height = 14)
ggplot(tmp, aes(x = location, y = last.game.loc, fill = log(N))) + 
    geom_tile() +
    facet_wrap(~lst.game + cur.game) + 
    labs(x = 'Current Game Location', y = 'Last Game Location', 
         title = 'Distribution of Next Day Opponent - MLB') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 315, vjust = 0.5),
          plot.title = element_text(hjust=.5))
dev.off()

##################################################
### Party by team location
##################################################
load(file = 'tmp_data/nmusician_estabs_mlb.RData')
tmp <- musicians[, list(party.continuous = mean(log(nmusicians+1))), 
                 by = team][order(party.continuous)][!is.na(party.continuous)]

pdf('writing/Party_by_Team_Location_mlb.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location: MLB',
     ylab = 'Log Avg of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
dev.off()

@@

pdf('writing/mlb_bets_by_season.pdf')
par(mfrow = c(3,2))
b <- lapply(2012:2016, function(yr) {
    m <- glm(I(team.score > opponent.score) ~ party + odds,
             data = mlb.lines[year(date) < yr], family = 'binomial')
    p <- predict(m, newdata = mlb.lines[year(date) == yr], type = 'response')
    idx <- which(p < .45)
    p1 <- mapply(Predict, prediction = p[idx], 
                 vegas = mlb.lines[year(date) == yr, odds][idx],
                 MoreArgs=list(threshold = 0.01))
    b <- mapply(Bet, our.prediction = p1,
                actual.outcome = mlb.lines[year(date) == yr, team.score > opponent.score][idx],
                odds = mlb.lines[year(date) == yr, odds][idx], SIMPLIFY = T)
    cat(paste0(sum(b, na.rm = T), '\n'))
    ### 
#    pdf(paste0('mlb_bets_', yr, '.pdf'))
    betting.days <- mlb.lines[year(date) == yr][idx, date]
    running.prof <- cumsum(ifelse(is.na(b), 0, b))
    plot(x = 1:length(b), y = running.prof, 
         main = paste0('Profits over the ', yr, ' season\n',
                       'Training on 2011-', yr-1, ' data'),
         xlab = 'Game Number', ylab = 'Profit', type = 'l')
    abline(a = 0, b = 0, lty = 3)
    points(x = which.min(running.prof), y = min(running.prof), type = 'p')
    text(x = which.min(running.prof), y = min(running.prof), 
         labels = round(min(running.prof)), pos = 4)
    return(b)
#    dev.off()
})
dev.off()
